%!TEX root = ./witches-of-weissbruck.tex
\chapter{Dramatis Personae}\label{ch:dramatis-personae}
This chapter provides background and statistics for some of the more important
NPCs who may appear in this adventure. Some of them are central to the plot,
while others may or may not be encountered depending on the heroes' actions.

\section{The Hedge Wizards of Lenzdorf}
Most rural areas of the Empire will be home to at least one Hedge Wizard. These
men and women use traditional and unlicensed magic to serve their communities
by providing medicine and keeping local spirits at bay. The villages of Lenzdorf
and Apfelbaum have been under the watchful eye of one such rural mage for
the last seven decades or more. Most of the villagers don't realise the full
extent of her work, coming to her only for herbal medicines. Hedge Wizards stay
far from the beaten track, because their magic is considered illegal by Imperial
authorities, and they risk arrest, torture, and death at the stake if
discovered. Fortunately, most villagers care too much for their local Hedge
Wizard to allow that to happen easily.

\subsection{Angela Trieste}
Angela Trieste, ``die Altfrau von Lenzdorf'', has lived on the outskirts of
Lenzdorf for all of her 65 years.
Her mother was hedgewise before her, and she's never known another life. She
enjoys her calling, both the seen and unseen aspects of it. Villagers come to
her for medicine and herbcraft, and she is much loved for that by the people of
Lenzdorf and Apfelbaum. She also wanders in the Hedge keeping watch over her
villages and fields, constantly on the look out for spirits or other malign
influences threatening her people. Occasionally, if the threat is too great,
she will send a villager to anonymously tip off the Sigmarite orders in the
nearby town of Weissbruck, though she's always careful to disguise the true
source of the information.

Her apprentice Hermann has been with her for seven years. She took him on in
the hopes of protecting him from the clutches of both Chaos and the Witch
Hunters, but has grown to love him like a son. She herself never had children,
and has developed an incredibly strong affection for her apprentice. Sadly, this
affection has blinded her to the growing influence of Chaos over her young
charge's heart\ldots

\statblockfullmagic{Angela Trieste, Hedgewise}
    {4 & 22 & 29 & 32 & 48 & 51 & 31 & 45 & 49 & 24 & 53 & 13}
    {Channelling (Hedgecraft)~+15, Cool~+10, Endurance~+5, Heal~+15,
        Intuition~+15, Language (Magick)~+15, Lore (Folklore)~+10,
        Lore (Herbs)~+15, Lore (Lenzdorf \& Apfelbaum)~+10, Lore (Spirits)~+15,
        Outdoor Survival~+10, Perception~+15, Trade (Herbalist)~+15}
    {Arcane Magic (Hedgecraft), Magical Sense, Petty Magic, Sixth Sense,
        Strider (Woodlands)}
    {Animal Friend, Dazzle, Entangle, Mirkride, Mundane Aura, Nostrum,
        Part the Branches, Protective Charm, Terrifying}
    {Antitoxin kit, Backpack, Dagger, Healing draught (2), Healing poultice (3)
        Lucky charms (7), Nightshade (1 dose), Quarterstaff, Trade
        tools (Herbalist), Vitality draught (1)}

\subsection{Hermann Rauch}
Hermann is Frau Trieste's 17-year-old apprentice. She took him to live with her
at the age of 9, when she saw his innate magical talent awaken at the same time
as a travelling Witch Hunter was passing through the village. Rather than risk
the child accidentally manifesting some magical ability and being burned, she
agreed with his parents that he should go to live with the old Hedge Master and
learn to control his talents. He never truly accepted the move, but over the
years he had seemed to make peace with his situation. In truth, his presence
turned out to be more of a blessing to the old wizard than to him.

Hermann's apparent toleration of his position came to an end while he was on an
errand in Weissbruck for his mistress. He took an instant liking to a merchant's
daughter, and na{\"\i}vely sought to impress her with a show of his magical
talents. Far from being impressed, the girl recoiled, ridiculing him as a
``filthy peasant conjuror'' and threatening to call the town watch. Hermann
fled, resentment and shame burning in his chest. Most teenagers face rejection
in their romantic lives, but unfortunately, Hermann's magical senses gave easy
access for the tendrils of the Chaos god Slaanesh to start winding themselves
around his heart. His bitterness and resentment grew, both towards the girl who
had rejected him and to his mistress Frau Trieste, who he blamed for his whole
sorry condition. As Slaanesh whispered in his mind, he developed a plan for
revenge on all those who had insulted and shamed him, one which he \textit{knew}
would force everyone to pay him the respect he deserved.

\statblockfullmagic{Hermann Rauch, Hedge Apprentice}
    {4 & 35 & 31 & 23 & 29 & 33 & 39 & 44 & 32 & 33 & 30 & 9}
    {Channelling (Daemonology)~+5, Channelling (Hedgecraft)~+5, Endurance~+5,
        Intuition~+5, Language (Magick)~+5, Lore (Folklore)~+5, Lore (Herbs)~+5,
        Outdoor Survival~+5, Perception~+5, Trade (Herbalist)~+5}
    {Arcane Magic (Daemonology), Petty Magic, Rover}
    {Careful Step, Dart, Manifest Lesser Daemon, Marsh Lights}
    {Backpack, Dagger, Lucky charms (4), Quarterstaff, Trade tools (Herbalist)}


\section{Order of the Purifying Flame Chapter House, Weissbruck}
The Witch Hunters' chapter house in Weissbruck currently houses just two
officers. It is normally the base of the district's Witchfinder General and two
permanently assigned Witch Hunters and a number of Interrogators, as well as
offering accommodation for any travelling members of the Order passing through.
A Beastman ambush some months ago killed the previous Witchfinder General and
the other staff, leaving just one Witch Hunter alive. Karina Str{\"o}m had been
left to oversee the district alone until the travelling Inquisitor Lukas Volf
arrived.

\subsection{Lukas Volf}
Lukas Volf is a broad-shouldered Nordlander, of average height but solidly
built. He is in his mid-40s, with short cropped brown hair and a long
moustache. He has been a witch hunter for the last 27 years, currently serving
in the office of Inquisitor. Rather than being bound to a particular district,
his role is to roam the Empire pursuing witches and heretics throughout Sigmar's
realm. He came to Weissbruck several months ago, chasing one of his targets,
but when the district's Witchfinder General was killed by Beastmen he
volunteered to step in and keep the chapter house running. He and the one
surviving Witch Hunter, Karina Str{\"o}m, have just about kept the peace despite
a greatly-reduced staff---Graf Sebastian himself has personally commended the
Inquisitor for his service.

What most others do not know is that Volf also belongs to a secret
society within his Order that has fallen into the worship of the Chaos god
Khorne. While most imagine Khorne's followers as crazed berserkers, anyone who
glories in killing and bloodshed draw his eye. Khorne's hatred of magic users
is well known to those with a knowledge of Chaos lore, and it is this aspect of
the Blood God that drew the worship of Volf and his fellows. They secretly
dedicate every witch they burn to him, even while they pretend to make prayer to
Sigmar. Whole villages have been burned by Volf to satisfy his brutal master's
lust for death and destruction. What his purposes in Weissbruck are remain to be
seen.

\statblockfull{Lukas Volf, Inquisitor}
    {4 & 36 & 40 & 32 & 47 & 29 & 34 & 37 & 30 & 44 & 42 & 15}
    {Charm~+5, Consume Alcohol~+10, Cool~+10, Gossip~+10, Heal~+5,
        Intimidate~+10, Intuition~+10, Leadership~+5, Lore (Chaos)~+10,
        Lore (Torture)~+5, Lore (Witches)~+10, Melee (Brawling)~+5,
        Perception~+5, Ranged (Crossbow)~+10, Ride (Horse)~+10}
    {Menacing, Read/Write, Seasoned Traveller}
    {Crossbow pistol (24 bolts), Daggers (4), Leaden charm, Riding horse,
        Saddle \& tack, Silvered sword, Torture instruments}

\subsection{Karina Str{\"o}m}
Karina is a Witch Hunter in her early 30s. She is currently the only Witch
Hunter residing in the chapter house in Weissbruck, after her colleague was
killed in the same ambush which claimed Witchfinder General Haublitz. She and
Inquisitor Volf have been doing their best to keep the district under control
while they wait for the Order's bureaucracy to assign replacements. Despite the
pressure, they have just about managed to keep on top of the demands placed on
them, thanks in no small part to Str{\"o}m's willingness to pay skilled
mercenaries to take some of the more routine work.

Karina is as hardline in the pursuit of her calling as most of her Order, but
she doesn't share the same implicit suspicion of non-Witch Hunters that many of
her colleagues do. She still believes that most citizens of the Empire are
decent folk overall, as opposed to the ``heretics-in-waiting'' that more jaded
Witch Hunters come to see them as. She serves as a Witch Hunter from a genuine
desire to preserve Sigmar's Empire, not from the blind hatred of witches (or
just of people) that fires some of her brothers and sisters.

\statblockfull{Karina Str{\"o}m, Witch Hunter}
    {4 & 35 & 37 & 30 & 35 & 26 & 28 & 30 & 39 & 32 & 12}
    {Charm~+5, Consume Alcohol~+5, Heal~+5, Intimidate~+5, Intuition~+5,
        Lore (Torture)~+5, Melee (Brawling)~+5, Perception~+5,
        Ranged (Gunpowder)~+5, Ride (Horse)~+5}
    {Coolheaded, Read/Write}
    {Pistol (24 shots), Leather jack, Riding horse, Saddle \& tack,
        Silvered sword, Torture instruments}

\subsection{Karl-Josef von Naal}
The chapter house in Weissbruck is currently giving accommodation to a
travelling Warrior Priest of Sigmar named Karl-Josef, who has become known as
``Vater Karl'' by the town's citizens.

\statblockfullreligious{``Vater'' Karl-Josef von Naal, Warrior Priest}
    {4 & 37 & 38 & 38 & 42 & 29 & 30 & 30 & 30 & 44 & 35 & 12}
    {Cool~+5, Dodge~+5, Endurance~+5, Heal~+5, Leadership~+5,
        Lore (Theology)~+5, Melee (Basic)~+5, Pray~+5}
    {Bless (Sigmar), Seasoned Traveller, Strong-minded}
    {Battle, Courage, Hardiness, Might, Protection, Righteousness}
    {\textit{None}}
    {Sigmarite text, Leather jerkin, Breastplate, Sigmarite pendant, Robes,
        Warhammer}

\section{Other Weissbruck notaries}
Weissbruck is of course home to many other people, some of better reputation
than others. This final section gives details of some citizens of Weissbruck
who are likely to figure in the heroes' activities in some way or another.

\subsection{``Schwarz'' Kristian}
Kristian Voss, better known as ``Schwarz'' Kristian (Black Kristian), is the
leader of the Wharf Street Gang. His nickname is in part due to his dark
Southlander complexion, and in part due to his vile temper when angered. His
crew is the smaller of the two main gangs in Weissbruck (the other being the
Gunnersbridge Thugs), but they have come to wield a lot more influence over the
city as a whole, thanks to Black Kristian's talent for bribery and politics.
Where the `Gunners' rely on intimidation and brute force to keep operating,
Kristian's `Wharfers' operate thanks to carefully placed bribes and patronage.
They keep a small number of senior Watchmen on their payroll, along with some
influential members of the town council; it's even rumoured that they somehow
have influence with Graf Sebastian himself.

\statblockfull{``Schwarz'' Kristian, Gang Boss}
    {4 & 37 & 27 & 44 & 43 & 27 & 31 & 25 & 25 & 36 & 34 & 12}
    {Bribery~+15, Charm~+10, Consume Alcohol~+5, Cool~+10, Dodge~+5,
        Endurance~+5, Evaluate~+10, Gossip~+10, Intimidate~+10, Leadership~+5,
        Lore (Weissbruck)~+10, Melee (Basic)~+10, Melee (Brawling)~+5,
        Ranged (Gunpowder)~+5, Stealth (Urban)~+10}
    {Criminal, Etiquette (Criminals), Fearless (Watchmen),
        Hatred (Incompetents), Street Fighting}
    {Knuckledusters, Leather jack, Hand axe, Mail shirt, Pistol (10 shots)}

\subsection{Graf Sebastian Altmark}
The feudal ruler of Weissbruck is Graf Sebastian, who has held the manor of
Weissbruck for the last 22 years. He's in his late 50s, but is remarkably fit
and active for his age, often hunting and hawking with his family and close
friends. He often duelled for fun when younger, and though he's restrained
himself now that he's the Graf, he still fences regularly.

Unlike many of his fellow nobles around the Reikland, Graf Sebastian is
actively interested in the running of Weissbruck and is keen for the town's
business to benefit him and his family. The town's council is notoriously
independent however, and so he's forced to exert his influence more subtly. He's
made alliances with a few of the leading members of the council, including
Burgomeister Sara G{\"a}rtner, offering finance and advice in exchange for
their pushing his agendas. Over the last few months he's also begun to make
contact with some of the gangs in Weissbruck.

\statblockfull{Graf Sebastian Altmark, Magnate}
    {4 & 50 & 35 & 38 & 36 & 40 & 32 & 38 & 26 & 33 & 42 & 12}
    {Bribery~+10, Charm~+10, Consume Alcohol~+10, Gamble~+5, Intimidate~+5,
        Language (Classical)~+5, Leadership~+10, Lore (Heraldry)~+5,
        Lore (Weissbruck)~+10, Melee (Fencing)~+10, Melee (Parry)~+10,
        Play (Flute)~+5, Ride (Horse)~+10}
    {Briber, Etiquette (Nobles), Noble Blood, Read/Write}
    {Foil, Main gauche, Riding horse, Saddle \& tack,
        Various jewellery (50GC), Weissbruck manor}

\subsection{Sara G{\"a}rtner}
Sara is one of the most prominent Burgomeisters in Weissbruck. She is in her
mid-30s, and many in Weissbruck are surprised and suspicious of how she has
obtained such a high degree of influence at such a young age. She is an
incredibly intelligent businesswoman, but she has also received a lot of
underhanded support from both Graf Sebastian and the Wharf Street Gang, support
that she herself has courted. She has flattered Graf Sebastian into believing
that she is a firm supporter of the nobility, and that her vision for Weissbruck
is to restrain the town council from any attempts to pull away from the Graf's
rule. Black Kristian, on the other hand, has a much simpler arrangement with
her: she helps push the authorities towards pressurising the
Gunnersbridge Thugs and ignoring the Wharfers, and in return the Wharf Street
Gang exerts pressure on businesses or politicians who might get in the way of
the Burgomeister's plans.

It was Sara's daughter Hannah who rejected young Hermann Rauch's
advances, setting him on his course of revenge. Neither Sara nor her daughter
have any inkling of the young Hedge Apprentice's plans, but needless to say, if
he was caught he would certainly suffer for his plans.

\statblockfull{Sara G{\"a}rtner, Burgomeister}
    {4 & 28 & 30 & 30 & 24 & 47 & 48 & 49 & 46 & 26 & 48 & 12}
    {Bribery~+10, Charm~+15, Climb~+5, Consume Alcohol~+5, Cool~+15, Drive~+5,
        Dodge~+5, Evaluate~+15, Gamble~+10, Gossip~+15, Haggle~+15,
        Intuition~+10, Lore (Law)~+15, Lore (Weissbruck)~+15, Perception~+15,
        Play (Flute)~+5}
    {Dealmaker, Embezzle, Etiquette (Servants), Read/Write}
    {Large townhouse with servants, Coach and footman, Chain of office, Dagger}
