%!TEX root=./witches-of-weissbruck.tex
\chapter{The Witches of Sch{\"a}delheim}\label{ch:adventure}

This chapter presents the full adventure, \textit{The Witches of
Sch{\"a}delheim}. It's divided into five \textit{Acts}, each of which contains
several \textit{Scenes}. The separate acts will all progress in order, but
the scenes within an act may occur in a different order from what is written,
based on the heroes' actions. Each scene will give an indication of how the
adventure could progress.


\section{Act One: Down the River}
The adventure begins with the heroes journeying downriver, \textit{en route} to
some destination.

\subsection{Scene One: On Board the \textit{Bessie Blue}}
The opening scene of the adventure has the heroes sat on a river barge sailing
down the Reik in the direction of Altdorf. Whether the heroes knew each other
before embarking, or whether they've met on board, is something for the players
to discuss amongst themselves. The nature of where they're all headed is also
up for discussion. The following should give the players an introduction to
their current setting.

\begin{callout}
You've been travelling for two days now on a small river barge named the
\textit{Bessie Blue}. Late autumn in the Reikland is always cold and damp, and
you've been very grateful for the heat made by the barge's small coal burner.
Most of the space on the barge is taken up by its cargo of logs, and so you've
been spending most of your time feeling rather cramped. The barge's master and
his mate generally don't bother to talk to you, not even in the evenings at the
canalside inns you've been staying in. Today's been slower going after the
barge's horse lost a shoe, and tonight's inn is nowhere in sight as it starts
to get dark\ldots{}
\end{callout}

Any native of the Old World could tell you that it's dangerous to be travelling
the countryside in the dark. Reiklander humans and any other character with the
\textbf{Lore (Reikland)} skill will know this automatically. This scene has
two purposes: For the characters to introduce themselves to each other (if this
is their first time adventuring together), and for them to start to get a bit
paranoid about what might be out to get them in the darkness.
